Exoplanet population inference and the rate of Earth analogs \\ from noisy, incomplete catalogs

### 2014-06-05 document/ms.tex
massive refactor
more discussion

Given our domain knowledge of how detection efficiency depends on the physical
parameters, the intuitive choice would be to measure the survey completeness
in radius ratio or signal-to-noise instead of period and radius.
It is also likely that a change of coordinates would yield a higher precision
result.
That being said, it is still correct to measure the completeness in period and
radius, and there are a few practical reasons for our choice.
The main argument is that since the radius uncertainties are dominated by
uncertainties in the stellar parameters, it is not possible to use the
published catalog (\citealt{petigura}) to compute constraints on radius
ratios.
In the future, this problem would be solved by publishing a representation of
\emph{the full posterior PDF for each object in the catalog}.
In this case, the most useful data product would be \emph{posterior samples
for each target's radius ratio and stellar radius}.

@@

The equivalent Figures for the radius distribution (integrated over period
bins) are shown in Figures~\figref{radius} and~\figref{linear-radius}.

Our constraint on the rate of Earth analogs (as defined in \sect{extrap}) is
in tension---even though our result has large fractional uncertainty---with
the result from \citet{petigura}.
This is shown in \fig{real-rate} where we compare the marginalized posterior
PDF for \gammaearth\ to the published value and uncertainty.
Quantitatively, we find that the rate of Earth analogs---the average number of
Earth-sized planets orbiting a Sun-like on a year-long period---is
\begin{eqnarray}
\gammaearth &=& 0.017^{+0.018}_{-0.009} \quad.
\end{eqnarray}
Converted to these units, \citet{petigura} measured $0.119_{-0.046}^{+0.035}$
for the same quantity (indicated as the vertical lines in \fig{real-rate}).

@@

% Just a little bit of semi-justified self-citation.
\bibitem[Ambikasaran \etal(2014)]{dfm-gp}
Ambikasaran, S., Foreman-Mackey, D., Greengard, L., Hogg, D.~W.,
\& O'Neil, M.\ 2014, \arxiv{1403.6015}

>>>>

Given our domain knowledge of how detection efficiency depends on the physical
parameters, the intuitive choice would be to measure the survey completeness
in radius ratio or signal-to-noise instead of period and radius.
It is also likely that a change of coordinates would yield a higher precision
result.
That being said, it is still correct to measure the completeness in period and
radius, and there are a few practical reasons for our choice.
The main argument is that since the radius uncertainties are dominated by
uncertainties in the stellar parameters, it is not possible to use the
published catalog (\citealt{petigura}) to compute constraints on radius
ratios.
In the future, this problem would be solved by publishing a representation of
\emph{the full posterior density functino for each object in the catalog}.
In this case, the most useful data product would be \emph{posterior samples
for each target's radius ratio and stellar radius}.

@@

The equivalent Figures for the radius distribution are shown in
Figures~\figref{radius} and~\figref{linear-radius}.
\Fig{radius} shows the log-radius occurrence rate integrated over various
logarithmic bins in period.
The distributions in each period bin are qualitatively consistent; the
rate is dominated by small planets (around two Earth radii) with potential
``features'' near $\radius\sim3\radius_\oplus$ and $\radius\sim
10\radius_\oplus$.
These features appear in every period bin and they were also detected---using
a completely different dataset and technique---by \citet{dong} and a similar
result is visible in the occurrence rate determined by \citet[][their Figure
7]{fressin-fp} at low signal-to-noise.
\Fig{linear-radius} shows the same result but presented as a function of
linear radius.
In these coordinates, the occurrence rate in a single bin is no longer
uniform; instead, scales as inverse radius.

Our constraint on the rate of Earth analogs (as defined in \sect{extrap}) is
in tension---even though our result has large fractional uncertainty---with
the result from \citet{petigura}.
This is shown in \fig{real-rate} where we compare the marginalized posterior
probability function for \gammaearth\ to the published value and uncertainty.
Quantitatively, we find that the rate of Earth analogs is
\begin{eqnarray}
\gammaearth &=& 0.017^{+0.018}_{-0.009} \quad.
\end{eqnarray}
Converted to these units, \citet{petigura} measured $0.119_{-0.046}^{+0.035}$
for the same quantity (indicated as the vertical lines in \fig{real-rate}).

@@

\bibitem[Ambikasaran \etal(2014)]{dfm-gp}
Ambikasaran, S., Foreman-Mackey, D., Greengard, L., Hogg, D.~W.,
\& O'Neil, M.\ 2014, \arxiv{1403.6015}
